\documentclass[10pt]{article}

\usepackage[hmargin=1.25cm, vmargin=.2cm]{geometry}   
\topmargin -2.5cm

% Font override
\renewcommand{\familydefault}{\sfdefault}
\usepackage{yplan}


% SYMBOLS - the ones you see on the left of the email and of the phone
\usepackage{marvosym}
\usepackage{soul}




% COLORS
\usepackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{headings}{HTML}{701112} 	%dark red



% Custom sections
\usepackage{titlesec}
\titleformat{\section}
	{\color{headings}
		\scshape\Large\raggedright}{}{0em}{}[\color{black}\titlerule]
\titlespacing{\section}{0pt}{0pt}{8pt}


\pagestyle{empty}  % Disable page numbers


\begin{document}

	\par{\centering
		{\sffamily\Huge \so{ERIC L. M. THOMAS}
	}
	\par \hfill
	\par \hfill


\begin{minipage}[t]{0.44\textwidth} %START of right-hand side minipage
	
	\vspace{0pt} %trick for alignment
	

	

\section{Education}

\begin{tabular}{rl}
 	
	%EDUCATION -1-
	\textsc{Spring} 2009 & Bachelor of Science: Computer Science\\
	 & \textsc{Rowan University}, Glassboro, NJ\\
	 & Specializations: Software Engineering,\\
	 & Information Technology,\\
	 & Programming Languages \& Compilers,\\
	 & Artificial Intelligence\\
	 &\normalsize \textsc{Gpa}: 3.551, Cum Laude

\end{tabular}\\

\section{Technical Skills} 

    \begin{tabular}{ll}
		Languages:	       & C/C++, Ruby, Tcl/Tk, Java, Python,\\
		                   & Perl, PHP, Scheme, bash, tcsh \\
		                   & \\
	    Systems: & Linux (Fedora, Ubuntu, RHEL), \\
	                       & Unix (AIX, Solaris), \\
	                       & Microsoft Windows (3.1 - Vista) \\
	                       & \\
	    Software:          & Version control(Git/Mercurial/SVN),\\
	                       & Development tools(vim, Eclipse), \\
	                       & Database systems(MySQL, SQLite), \\
	                       & Web servers(Apache, mongrel), \\
	                       & many Unix utilities. \\
	                       & \\
	    Miscellaneous:     & Rails, XML, YAML, HTML5, \\
	                       & REST, regular expressions
	\end{tabular}
	

\section {Projects}
  {\bf drum-tabber} \hfill Spring 2009 \\
    A multi-threaded Java application that decrypts MIDI signals from an electronic drum kit
    and converts them to drum tablature (music notation represented with ASCII text). \\

  {\bf arimaai} \hfill Spring 2009 \\
    Co-developed an AI bot in Python and Psyco to explore various search algorithms implemented
    for Arimaa, a board game that has proven to be more difficult for computers than chess. \\
    
  {\bf WebGPS} \hfill Fall 2008 \\
    Real-time interactive web visualization tool which 
	graphically displays the hierarchy structure of a web page. \\

  {\bf FlightGUI} \hfill Spring 2008 \\
    Served as team leader on a collaborative project between Rowan University and Fairfield University
    to develop FlightGUI, an application that calculates and graphically displays readings of flights in conflict. \\
   
\section{AWARDS}
  \begin{itemize}  \itemsep -2pt \normalsize
    \item Upsilon Pi Epsilon International Computer Science Honor Society
    \item Chi Alpha Sigma National Athletic Honor Society
    \item Edward J. Bloustein Scholarship
  \end{itemize}

\end{minipage}
\hfill
\begin{minipage}[t]{0.52\textwidth}

	\vspace{0pt}	%trick


% <<<< NEW SECTION >>>>	
\section{Professional Experience}

	% FAA - START

	{\large Computer Scientist} \hfill Spring 2009 to Present\\
	\emph{Federal Aviation Administration, Pomona, NJ}\\[5pt]
	\normalsize{Currently working with a rapid prototyping team that coordinates with human factors experts to prototype new air traffic control systems.}
	\begin{itemize}  \itemsep -2pt \normalsize
      \item Redeveloped DataLink, a simulated "text messaging" system between controller and pilot to replace voice-only communications.
      \item Wrote various data capturing plugins to calculate air traffic within a given region of airspace. 
      \item Converted system from 32 bit to 64 bit architecture.
      \item Created custom supervisor and test suite GUIs.
      \item Configured system to utilize the Boost C++ libraries.
    \end{itemize}
	% FAA - END
	
	% ROWAN - START
	{\large Researcher} \hfill Winter 2008 to Spring 2009\\
	\emph{Rowan University, Glassboro, NJ}\\[5pt]
	\normalsize{Co-developed a unique concept of data analysis to compare aircraft trajectory prediction tools. \\
	            Paper: \emph{Enhanced Star Glyphs for Multiple-Source Data Analysis}; presented at 13th International Conference on Information Visualization (IV), 2009.}\\
	% ROWAN - END
	
	
	% COOP - START
	{\large Student Co-op} \hfill Spring 2008 to Summer 2008\\
	\emph{Federal Aviation Administration, Pomona, NJ}
	  \begin{itemize}  \itemsep -2pt \normalsize
      \item Developed application to read and parse a live data stream
            of the position and flight plans of all aircraft in the National Airspace System.
      \item Wrote an inventory management system in PHP/MySQL.
      \item Performed network configuration of a research and testing laboratory.
      \item Installed and managed an Apache HTTP server.
	\end{itemize}
	% COOP - END
	
\section{Community Service}  
  \begin{itemize}  \itemsep -2pt \normalsize
      \item Served as a teacher of web design and development for a non-profit  organization that provides 
            creative programs to the youth in Camden City. The program was featured on NBC's 10! show.
      \item One of three judges for the math category at the Jersey Shore Science Fair.
  \end{itemize}
  
\section{Hobbies} Competitive runner, board game aficionado, parsing expression grammar dabbler. \\


	
\section{Contact}
	\begin{tabular}{cp{8.1cm}}
		\raisebox{-1pt}{\Large\Letter}  & 138 Wahwahtaysee Trail Medford Lakes, NJ 08055 \\
		\raisebox{0pt}{\Large\Telefon} & \so{(609)744-3419} \\
		\raisebox{0pt}{\Large\Email}   & \so{eric.l.m.thomas@gmail.com} \\
		\raisebox{-1pt}{\Mundus}       & \so{www.elmthomas.com}
	\end{tabular}


\end{minipage}


\end{document}
